---
title: "Homework: Reproducibility and Professional Communication"
execute:
  error: true
author: "Joycelyn Ayensu"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```


# Reproducible Examples & Debugging

In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```
 add <- function(str) {
      meals <- append(meals, as.character(str))  
    }
```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 


---

1. Are the question and problem description complete?

> <! I think the problem and question is partially complete. 
The user describes the function’s purpose (to append a string to a vector meals) and says it “does not work,” but the description lacks crucial details such as if there an error message,How the user is calling the function, what meals looks like before and after running the function, What do they expect vs. what actually happens? -->






2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <! No, not fully reproducible.The function alone can be copied, but it cannot run successfully because meals is undefined in the function’s environment. -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <! yes, the function itself is minimal.it successfully avoids extra details but omits essential setup code needed to reproduce the issue.

4. Does the question describe any attempted solutions?

> <! No. There's no mention of any alternative approaches tried
or Debugging steps taken -->


Debugging the error,
```{r}
meals <- c("breakfast", "lunch")

add <- function(meals, str) {
  meals <- append(meals, as.character(str))
  return(meals)
}

# Call the function and reassign the result
meals <- add(meals, "dinner")

# Check the result
print(meals)


```

## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about — a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)


---

1. Are the question and problem description complete?

> <! Yes, very complete. The user provides excellent context that they are a beginner in a Coursera course, this is their first function, it returns NA when called but works when steps are run individually. They show both the error and what they expected. -->

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <! Partly reproducible. Missing the actual CSV data files from the /Users/mike******/Desktop/ directory. 
However, the bug is visible in the code itself, so an experienced R user can debug it without the data.
Reproducibility could improve by using the directory argument instead of a hard-coded path as well as sharing a tiny CSV snippet and and showing names(z) or str(z) to reveal column names/types.-->



3. Is the example minimal? Does it include extra code or information that is not necessary?

> <! Yes, it's minimal. Shows only the failing function, the function call, error message, and working manual code. Nothing extraneous. -->

4. Does the question describe any attempted solutions?

> <! Yes. The user demonstrates they debugged by running the steps manually outside the function, which worked. This shows good problem-solving effort for a beginner -->



## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

---

1. Are the question and problem description complete?

> <! I think its partly complete because the user stated the exact error, context (knitting an Rmd), and the relevant line. Missing: a tiny data snippet (e.g., dput(head(Gastropods))) and the exact code chunk where filter() is called with package loads. -->

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <! Not fully reproducible. It depends on an external CSV (MaroubraZones.csv) and the users local project. 
To improve, i will suggest the user attaches a 5–10 row sample via dput() or use a built-in dataset with a mock filter, so anyone can reproduce. -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <! Close, but can be trimmed. The user only needs the package loads and the single failing line; plots and other chunks are not necessary. -->

4. Does the question describe any attempted solutions?

> <! I think the solution is limited. The user mentions checking for spelling errors and verifying the column and values exist. No mention of trying alternative syntax, checking documentation, or isolating which specific line causes the error. -->




## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

---

1. Are the question and problem description complete?

> <! Yes. The user clearly describes what the program is supposed to do (“calculate the cost for shipping”), what’s actually happening (“it always prints $6 or $8”), and provides both input examples and the full code snippet. That is a complete problem statement. -->

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

> <!Yes, it’s fully reproducible — anyone can copy and run the code in Python.
The only missing piece is the Python version (since raw_input() is Python 2 syntax). It would help to mention that the problem is seen in Python 2 and confirm the intended data types. -->

3. Is the example minimal? Does it include extra code or information that is not necessary?

> <! Yes. It is short, focused, and contains only what is needed to show the error (no extra variables or unrelated functions). -->

4. Does the question describe any attempted solutions?

> <! Slightly. The user mentions they “can’t get past that” and observed that the same shipping cost appears each time, but doesn’t specify debugging attempts (e.g., checking variable types or printing intermediate values). -->


# Professional Communication

## Slides

Create a set of quarto slides in the file slides.qmd. 

Set two different output formats - for instance, reveal.js and beamer. 

In your slides:

- Introduce yourself and show a picture of yourself
- Provide basic biographical information: birthday, where you grew up
- Show a picture of your favorite animal
- Provide your favorite plot, generated in either R or python. (This can be one you've generated in this class). Ensure that the code does not show, but the plot does.
- Provide a link to your CV, which you will generate in the next part.

## CV

Select a CV template that uses either LaTeX or Markdown:

- https://github.com/kazuyanagimoto/quarto-awesomecv-typst
- https://github.com/schochastics/quarto-cv
- https://www.overleaf.com/latex/templates/tagged/cv

Use the template to create a curriculum vitae that has your education, work experience, and any other sections you would like to include. Compile your CV and link to it in your slides. 
